\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-09-17 paper.tex
Revise until conclusions

From Eq. \eqref{Eq:J} we evaluate the
normalized current density $j_\perp/I$ expected at the positions $n$ indicated in
Fig. \ref{fig:SI3}.
(Table \ref{t:xj}).
\begin{table}
  \centering
  \begin{tabular}{rrr}
    \(x'\)(cm) & \(x\)(cm)& \(j_\perp/I\) (\(\text{cm}^{-2})\)\\
    from edge& from wall&\\
    \hline
    0.2 & 0.06 & 0.7219\\
    0.4 & 0.26 & 0.6723\\
    0.6 & 0.46 & 0.5769\\
    0.8 & 0.66 & 0.4645\\
    1.0 & 0.86 & 0.3599\\
    1.2 & 1.06 & 0.2749\\
    1.4 & 1.26 & 0.2112\\
    1.6 & 1.46 & 0.1666\\
  \end{tabular}
  \caption{Normalized current density expected at different positions on
    different samples.}
  \label{t:xj}
\end{table}

@@

@@

We measured the reflectance spectra of sample $G_3$ at the positions
indicated in Fig. \ref{fig:SI3}. The results are shown in
Fig. \ref{fig:R20}.
We fitted the reflectance measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity $p$, and the thickness of the
film  $d$ as
adjustable parameters. We also fitted a scaling parameter $s$ to allow
for calibration variations among spectra. From the thickness we
obtained the etching rate $v=d/t$. Notice that the fit is reasonably
good. The contrast of the reflectance in the experiment is smaller
than the fit. We believe this is due to the finite width
\notaL{beams width=?} of the illuminating beam of our
spectrometer. Thus, as our GRIN sample is not homogeneous, the
experimental results show an average over regions with slightly
different porosities and thicknesses, averaging out the interference
maxima and minima. This is most notable for the thicker regions
towards the left side of Fig. \ref{fig:SI3} and for smaller
wavelengths. Similar remarks apply to the fits to the reflectance
spectra of the other samples, incorporated in our supplemental
material (Figs. \ref{fig:R5} and \ref{figR10}).
The results obtained from the reflectance fits are summarized in table
\ref{t:jpdv}.

\begin{table}
\centering
\begin{tabular}{lrrrrrr}
  Sample & current &  density \(j\) & porosity &
  thickness & scale \(s\)& etching rate\\
       & $I$ (mA)      & $j$ ($\text{mA}/\text{cm}^2$) & $p$
       & $d$ ($\mu\text{m}$) & $s$ & $v$ (nm/s)\\
\hline
$G_1$ & 5  & 3.609 & 0.4943 & 0.3402 & 0.8493&  1.3608 \\
      &    & 3.361 & 0.5713 & 0.3895 & 0.9789&  1.558  \\
      &    & 2.884 & 0.5657 & 0.3312 & 0.9569&  1.3248 \\
      &    & 2.322 & 0.5555 & 0.2732 & 0.9536&  1.0928 \\
      &    & 1.799 & 0.5592 & 0.2236 & 0.9951&  0.8944 \\
      &    & 1.374 & 0.5557 & 0.1886 & 0.9729&  0.7544 \\
      &    & 1.056 & 0.5491 & 0.1512 & 0.9606&  0.6048 \\
      &    & 0.833 & 0.5519 & 0.1238 & 0.9897&  0.4952 \\
$G_2$ & 10 & 7.219 & 0.5910 & 0.6347 & 0.8559&  2.5388 \\
      &    & 6.723 & 0.6437 & 0.6934 & 0.9914&  2.7736 \\
      &    & 5.769 & 0.6383 & 0.5907 & 0.9523&  2.3628 \\
      &    & 4.645 & 0.6265 & 0.5327 & 0.9798&  2.1308 \\
      &    & 3.599 & 0.5991 & 0.4587 & 0.9389&  1.8348 \\
      &    & 2.749 & 0.5902 & 0.4044 & 0.9449&  1.6176 \\
      &    & 2.112 & 0.5753 & 0.3378 & 0.9361&  1.3512 \\
      &    & 1.666 & 0.5711 & 0.2958 & 0.9481&  1.1832 \\
$G_3$ & 20 & 14.438& 0.6860 & 1.2044 & 1.1491&  4.8176 \\
      &    & 13.44 & 0.7129 & 1.1931 & 1.0767&  4.7724 \\
      &    &11.538 & 0.7031 & 1.0443 & 1.0588&  4.1772 \\
      &    & 9.29  & 0.6258 & 0.7516 & 1.0063&  3.0064 \\
      &    & 7.198 & 0.6247 & 0.5380 & 1.0104&  2.152  \\
      &    & 5.498 & 0.5927 & 0.4387 & 0.9625&  1.7548 \\
      &    & 4.224 & 0.5844 & 0.3633 & 0.9625&  1.4532 \\
      &    & 3.332 & 0.5909 & 0.3392 & 1.0112&  1.3568 \\
\end{tabular}
\caption{\label{t:jpdv}
  Names of data files, current, current density and fitted parameters:
  porosity, thickness and scale factor.}
\end{table}

\ifinclude
We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
$p_{1C}= 0.40$. The fitted reflectance has a good agreement with the
measured one, though its interference oscillations are larger towards
the blue region probably due to the lack of surface scattering in our
calculation. We also show in Fig. \ref{fig:DR3} the wavelength dependence of
the complex index of refraction corresponding to the fitted porosities.
Similarly, for a second sample $G_2$, etched with a
larger current $I_2 =40 \,\text{mA}$, for a time $t_2=$?\notaL{El ancho no
  tiene sentido si no especificas el tiempo} we obtained the
depths $d_{2A}=1950\,\text{nm}$, $d_{2B}=1690\,\text{nm}$, and $d_{2C}=
1430\,\text{nm}$, and the corresponding porosities \notaL{las posiciones ¿fueron las mismas que para $G_1$?}, $p_{2A}= 0.76$, $p_{2B}=
0.73$, and $p_{2C}= 0.68$.

\begin{figure}
  \centering
   \includegraphics[width=\textwidth]{Images/grinJDR}
  \caption{(a)Current density calculated by scaling the results of
    Fig. \ref{fig:DR1} by the currents $I_1=5\text{mA}$ and
    $I_2=40\text{mA}$ used to prepare samples $G_1$ and $G_2$.
. \notaL{Pon paréntesis de ambos
      lados (a) y (b). El eje horizontal es $x$, no $a$. El eje
      vertical es $j_\perp$.}
    (b)Etching rate speed $v=d/t$ obtained at different positions $A$, $B$,
    and $C$ over samples $G_1$ and $G_2$, where $d$ is the thickness
    as measured from SEM micrographs, as in Fig. \ref{fig:DR4},
    and $t$ is the etching time.\notaL{Falta una gráfica similar de
      porosidad vs. x para las dos muestras}\notaL{Las escalas del
      lado derecho no tienen que ver con las del lado
      izquierdo. Deberías poner la misma escala de ambos lados, con el
    mismo quiebre.}\notaL{Sugiero en la gráfica de la corriente
    graficar las dos líneas completas, además de los 6 puntos
    correpondientes a A, B y C de las dos muestras}}
  \label{fig:JDR}
\end{figure}

In Fig. \ref{fig:JDR}(a) we show the current density
$j_\perp$ obtained from Fig. \ref{fig:DR1} by scaling by the actual
current $I_1=5\,\text{mA}$ and $I_2=40\,\text{mA}$ employed to prepare
samples $G_1$ and $G_2$, respectively (Eq. \eqref{Eq:J}). We indicate the values
corresponding to positions $A$, $B$, and $C$ on the samples.
In Fig. \ref{fig:JDR} (b) we show the etching rate $v = d/t$ on
selected positions of both samples obtained by dividing the thickness
$d$ measured as in Fig. \ref{fig:DR4} by the etching time.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/grinJD31}
  \caption{(a) Etching rate $v$ and (b) porosity $p$ as a function of the
    density current $j_\perp$, obtained from Fig. \ref{fig:JDR}. We
    show the data points and the results of power
    law fits, yielding $v=0.68j_\perp^{0.69}$ and
    $p=0.33j_\perp^0.21$, \notaC{cambie las expresiones $v=0.53j_\perp^{0.79}$
    and $p=0.3j_\perp^0.24$}
    with corresponding correlation coefficients
      $r_v^2=0.951$ and $r_p^2=0.989$ \notaC{ tambien cambie $r_v^2=0.993$
      and $r_p^2=0.0.847$ }(here $v$ is in nm/s, $p$ is
      dimensionless and $j_\perp$ is in mA/cm$^2$). \notaL{cambia J por $j_\perp$, V por $v$ y P
      por $p$. Quita el letrero fitting data, la ecuación y el valor
      de $R^2$}\notaL{Los ajustes ¿son correctos con estas unidades?}}
  \label{fig:Indr1}
\end{figure}
By relating among themselves the panels of Fig. \ref{fig:JDR} we
may obtain the etching rate $v$ and the porosity $p$ as
functions of the current density $j_\perp$. The results are shown in
Fig. \ref{fig:Indr1}.\notaL{\ldots Apenas aquí dijiste cuál fue el
  tiempo de ataque de la muestra dos: relating to depth and time ($
  200 \ \ s $ ). ¿Es correcto este tiempo? Ponlo en su lugar}
We fitted the data points with simple power laws and found
\begin{equation}
  \label{eq:etch}
  v=0.68j_\perp^{0.69} \notaC{cambie v=0.53j_\perp^{0.79}}
\end{equation}
and
\begin{equation}
  \label{eq:poros}
  p=0.33j_\perp^{0.21}, \notaC{cambie p=0.3j_\perp^{0.24}}
\end{equation}
where $v$ is
expressed in nm/s, $p$ is dimensionless and $j_\perp$ is expressed as
mA/cm$^2$. The corresponding correlation coefficients are $r_v^2=0.951$
and $r_p^2=0.847$. \notaC{cambie $r_v^2=0.993$
and $r_p^2=0.989$.}
\notaL{Digresión teórica. El producto $pv$ es
  proporcional a la cantidad de materia removida por segundo. En mi
  opinión, esto debería ser proporcional a la corriente $pv\propto
  j_\perp$. ¿Es correcto? A tí te sale algo parecido pero no
  exacto. ¿Se podrá hacer un mejor ajuste tomando esto en cuenta?
  ¿Alguien lo ha discutido en la literatura?}\notaL{En todo caso, todo
  esto se tiene que rehacer usando la expresión teórica correcta y las
  posiciones correctas}

Fig. \ref{fig:Indr1} illustrates an advantage of using a cell
geometry for which the current density may be obtained
analytically. Namely, we can relate the etching rate and the
porosity to the current density by taking measurements at
different positions along just a few PS GRIN samples. Thus, it is much easier
and faster to obtain calibration curves which are useful in the
fabrication of PS photonic structures, GRIN or otherwise.
\fi %include
\notaL{Removí lo de grinMC}
\ifinclude
\subsection{PS GRIN Microcavities}
\label{sec:grin-porous-silicon}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/MicrGrin}
  \caption{\notaL{Está bonita la figura, pero tiene errores. La
      superficie del electrolito y la superficie de la muestra
      deben ser ambas horizontales. Cambia la fuente por fuente
      de corriente. La punta del electrodo no debe ser una
      bola. Quita todo lo que está abajo del sustrato. Mejor pon
      solamente una H en alguna región amarilla y una L en
      alguna región azul. El electrolito tiene gotas o
      burbujas. Tal vez sea mejor ponerle un color uniforme. Quita los
      anchos totales, pues no creo que nos sean útiles. Haz que los cables
      horizontales sean horizontales.}
    PS GRIN microcavity made of layers of high (H) and low (L)
    refractive index $n_H$ and $n_L$ and widths $d_H$ and $d_L$
    arranged in the sequence $(HL)_NHH(HL)_N$. \notaL{CUánto vale $N$?
    Antes habías dicho que 6, pero en la figura 12 parece otra cosa} Both the index of
    refraction and the widths depend on position along the
    sample and are chosen to obey a quarter wavelength
    condition at a given position $A$ and wavelength $\lambda_c$.
  }
  \label{fig:MCGRIN0}
\end{figure}

As a simple application of our preparation and calibration methods, we
prepare a PS GRIN microcavity (MC), as illustrated in
Fig. \ref{fig:MCGRIN0}.  Alternate layers of relatively high (H) and low and low
(L) refractive indices $n_H$ and $n_L$, of corresponding thicknesses
$d_H$ and $d_L$, are prepared by alternatingly etching a Si sample in our
electrolytic cell with a current $I_H$ during a time $t_H$ and with a
current $I_L$ during a time $t_L$. We chose the currents $I_H=5\,\text{mA}$
and $I_L=40\,\text{mA}$ \notaL{¿son correctos estos valores?}, the same
that were used above to prepare samples $G_1$ and $G_2$.
We chose the etching times to obtain a MC at the given
position $A$ tuned to a given wavelength
$\lambda_c=0.67\mu\,\text{m}$. Thus, we chose the thicknesses so they
correspond to quarter wavelength plates, $n_Hd_H=n_Ld_L=\lambda_c/4$,
at this position and wavelength, yielding $n_H =2.6$,\notaL{Por qué no
  coincide con el dato de la tabla 1?} $p_H =0.46$,
$d_H=0.066\mu\text{m}$, $t_H=35\text{s}$, $n_L= 1.4$, $p_L =0.75$,
$d_L=0.117\mu\text{m}$, $t_L=11\text{s}$.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/MCGRIN2}
  \caption{(a)Top view photograph of a PS GRIN MC showing the position
    of the three measuring points $A$, $B$ and $C$. The cavity was
    tuned to the wavelength $\lambda_c=0.67\mu\,\text{m}$ at position
    $A$ (see text). We chose $x_A=0.3\,\text{cm}$, $x_B=0.8\,\text{cm}$,
    and $x_C=1.2\,\text{cm}$. (b-d) Reflectance spectra measured and
    calculated at positions $A-C$. For the calculation, the porosity
    and etching rates were obtained from Fig. \ref{fig:Indr1},
    the dielectric functions and indices of refracton from
    Eqs. \eqref{Eq:Brugg} and the reflectance from standard transfer
    matrix theory. \notaL{Quizás haya que usar D E F en lugar de A B
      C, pues A B C se usó para otras posiciones sobre la muestra
      $G_1$ y $G_2$. ¿Son correctas las posiciones aquí?}}
  \label{fig:MCGRIN3}
\end{figure}

\begin{table}
  \begin{tabular}{ccccccc}
    \hline
    Pos.(kind)&Curr. dens.(mA/cm$^2$)&Porosity&Index&Wavelength($\mu\text{m}$)\\
    \hline
    \hline
    A(H) & 5.5 & 0.45& 2.66& 0.65   \\
    A(L) & 44  & 0.74& 1.44& 0.65   \\
    B(H) & 4.0 & 0.41& 2.76& 0.58   \\
    B(L) & 32  & 0.68& 2.29& 0.58   \\
    C(H) & 3.0 & 0.39& 2.81&0.54    \\
    C(L) & 24  & 0.64& 2.30&0.54    \\
  \end{tabular}
  \caption{Some properties of the PS GRIN MC corresponding to the
    positions $A$, $B$ and $C$ and the corresponding high ($H$) and
    low ($L$) index layers. The current densities were obtained by
    scaling the results in Fig. \ref{fig:DR1} with $I_H$ and
    $I_L$, the depths were obtained from the etching
    times and the current density using \eqref{eq:etch}, the porosity
    was obtained from Eq. \eqref{eq:poros}, the indices of refraction
    were obtained from Eq. \eqref{Eq:Brugg} using the porosity, and
    the resonant wavelengths of the cavity were read from
    Fig. \ref{fig:MCGRIN3}.
    \notaL{Inventé lo de arriba. Qué es cierto y qué
      mentira?}\notaL{Por qué resuenas en 0.65 si habías diseñado
      0.67 en A?} \notaL{¿De dónde sacaste
        $\lambda_c$ para los otros puntos? ¿Cómo le hiciste para que
        $\lambda_c$ diera lo mismo en $H$ y en $L$? $n$ y $k$ dependen de la
        frecuencia. ¿Qué frecuencia usaste para darles valores en esta
        tabla?}\notaL{quité digitos a n. quité k pues es chiquita,
        ¿no? quité los tiempos pues son los mismos. Quité las
        posiciones pues están descritas antes. Añade una columna
        con las profundidades $d_H$ y $d_L$. }\notaL{De los rótulos de
      la figura quita las palabras Point. Cambia simulation por Theory.}}
	\label{tabla:1}
\end{table}
In Fig. \ref{fig:MCGRIN3} we show a photograph of a PS GRIN MC
sample, which displays a color that shifts towards the blue when we
move towards its right, that is, away from where the electrode was
positioned. In the figure we indicate three points with $x$ coordinates
$x_A=0.3\,\text{cm}$,  $x_B=0.8\,\text{cm}$, and $x_C=1.2\,\text{cm}$
on which we measured the reflectance spectra, also shown in the figure.
\notaL{Estas $x_A$ y $x_B$ son iguales a las anteriores, pero $x_C$
  no. ¿Es correcto? Me dice que sí, pues no podría irse al
  ultravioleta} \notaL{No dices cómo hiciste las curvas teóricas. Ya
  me explicó. {\bf la teoría es trampa} Dado el mínimo de reflectancia
medido, calculó una microcavidad {\em diseñada} para ese mínimo, en
lugar de usar los anchos predichos} The
spectra have the
expected shape: a high reflectance plateau corresponding to the
photonic band gap of the Bragg mirrors, with a deep narrow minimum due
to the Fabry-Perot resonance of the cavity. We also present the
calculated spectra. To that end, we calculated the current density
using the theory developed in Sec. \ref{sec:calc-curr-dens}, i.e., by
scaling Fig. \ref{fig:DR1} with the total current $I_H$ and $I_L$ used
to fabricate each layer. From the current densities we obtained the
corresponding etching rates and the porosities using
Eqs.~\eqref{eq:etch} and  \eqref{eq:poros}, and from them, the
thickness of each layer, the index of refraction
(Eq. \eqref{Eq:Brugg}) and the reflectance,using standard transfer
matrix theory \notaL{ref}. \notaL{Esto sería innecesario para los
  puntos A y B, aunque tal vez sí se necesita para C, oyes $x_C$
  parece ser distinto.}
Notice the good agreement between theory
and experiment. \notaL{No me lo creo. Me sospecho que más bien,
  ajustaste el experimento no sé con qué parámetro. Explícame cómo
  hiciste el cálculo.} The parameters used are shown in Table \ref{tabla:1}.
\notaL{No entiendo qué quisiste decir aquí: For theoretical values, we
  use complex refractive indices as free parameters to fit the
  experimental refractive spectra (Section 4.2).} The band-gap, the
resonance and the oscillations due to multiple reflections in the
region of transparency are similar, though the experimental spectra is
more rounded and the central resonance is wider. This might be due to
the roughness of the interfaces, which would lead to some scattering
whose effects are similar to those of an additional absorption
\notaL{cita el artículo en prensa de Guille y mío}.\notaL{Checar que no
  diga mentiras arriba. El ajuste es demasiado bueno, pero no sé cómo
  se hizo. Hay que explicar qué significan y de dónde salieron las
  $\lambda_c$ de la tabla. }

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Images/MCGRINSEM}
   \caption{Cross section SEM images corresponding to the positions
     $A$, $B$, and $C$ of the PS GRIN MC shown in
     Fig. \ref{fig:MCGRIN3}. The total thickness of the system at
     different positions, $d_A=2.25\mu\,\text{m}$,
     $d_B=2.17\mu\text{m}$, and $d_C=1.87\mu\text{m}$ are
     indicated. \notaL{Porque se ve una capa más ancha a la izquierda?
       ¿Por qué el número de capas arriba no es igual que abajo? ¿Por
       qué el número de capas no es el mismo en las distintas fotos?
       ¿Por qué no es 6 como dice el texto en la
       Sec. \ref{sec:fabrication-grin-ps}?}
     }
   \label{fig:MCGRIN4}
 \end{figure}
In Fig. \ref{fig:MCGRIN4} we show SEM cross-sectional images of
the PS GRIN MC sample. We can appreciate a relatively small interface
roughness and a clear contrast between the high and low porosity
layers. The structure of the microcavity is also visible, with a
central layer of twice the thickness of the corresponding layers
within the Bragg mirrors. The gradient of the thickness is also
evident, as $d_A>d_B>d_C$, with $d_A=2.25\mu\text{m}$,
$d_B=2.17\mu\text{m}$, and $d_C=1.87\mu\text{m}$ the total thickness
of the structure measured at the positions $A$, $B$, and $C$.
The measured thickness are in good agreement with those computed from
the current densities and the etching times $N(d_H+d_L)+2 d_H$ using
Eq. \eqref{eq:etch}, where $N$ is the number of pairs of layers in the
Bragg mirrors, which yield $d_A=2.31\mu\text{m}$,
$d_B=2.08\mu\text{m}$, and $d_C=1.65\mu\text{m}$. \notaL{Por qué una
  te dio más grande y las otras más chicas? Aquí tienes que decir
  cuánto vale $N$ y no has dicho cuánto valieron $d_L$ y $d_H$}
\fi %include

@@

\section{Supplementary material}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R5vslambda}
  \caption{Reflectance spectra at different positions
    on sample $G_1$ (shown in Fig. \ref{fig:SI3}), where
    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R5}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R10vslambda}
  \caption{Reflectance spectra at different positions
    on sample $G_2$ (shown in Fig. \ref{fig:SI3}), where
    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R10}
\end{figure}

>>>>

From Eq. \eqref{Eq:J} we evaluate the
normalized current density $j_\perp/I$ expected at the positions $n$ indicated in
Fig. \ref{fig:SI3}.
(Table \ref{t:xj}).
\begin{table}
  \centering
  \begin{tabular}{rrr}
    \(x'_n\)(cm) & \(x\)(cm)& \(j_\perp/I\) (\(\text{cm}^{-2})\)\\
    from edge& from wall&\\
    \hline
    0.2 & 0.06 & 0.7219\\
    0.4 & 0.26 & 0.6723\\
    0.6 & 0.46 & 0.5769\\
    0.8 & 0.66 & 0.4645\\
    1.0 & 0.86 & 0.3599\\
    1.2 & 1.06 & 0.2749\\
    1.4 & 1.26 & 0.2112\\
    1.6 & 1.46 & 0.1666\\
  \end{tabular}
  \caption{Normalized current density $j_\perp/I$ expected at different positions $x'_n$.}
  \label{t:xj}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R5vslambda}
  \caption{Reflectance spectra at different positions
    on sample $G_1$ ($I_1=5\,\text{mA}$), where
    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R5}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R10vslambda}
  \caption{Reflectance spectra at different positions
    on sample $G_2$ (shown in Fig. \ref{fig:SI3}), where
    $x'_n=0.2-1.6\,\text{cm}$ and $y=0.74\,\text{cm}$. We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R10}
\end{figure}

@@

We measured the reflectance spectra  at the positions indicated in
Fig. \ref{fig:SI3} on our three samples $G_1$, $G_2$,
and$G_3$, prepared using the same procedure
(Sec. \ref{sec:fabrication-ps-grin}) but applying different currents
$I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$, and $I_3=20\,\text{mA}$, . The results are shown in
Figs. \ref{fig:R5}, \ref{fig:R10}, and \ref{fig:R20}.
We fitted the reflectance measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity $p$, and the thickness of the
film  $d$ as
adjustable parameters. We also fitted a scaling parameter $s$ to allow
for calibration variations among spectra. From the thickness we
obtained the etching rate $v=d/t$ at each position. Notice that the fit is reasonably
good. The contrast of the reflectance in the experiment is somewhat smaller
than in our fitted curves. We believe this is due to the finite width
\notaL{beams width=?} of the illuminating beam of our
spectrometer. Thus, as our GRIN sample is not macroscopically homogeneous and its
properties have a gradient, the
experimental results have contributions from regions with slightly
different porosities and thicknesses, averaging out the interference
maxima and minima. We also expect microscopic inhomogeneities such as
interface roughness that might also reduce the contrast.
This is most notable for the thicker regions
towards the left side of Fig. \ref{fig:SI3} and for smaller
wavelengths.

The results obtained from the reflectance fits are summarized in table
\ref{t:jpdv}. Notice that the scaling parameters are close to 1,
showing that the calibration was adequate. \notaL{Is this meaningful?}.

\begin{table}
\centering
\begin{tabular}{lrrrrrr}
  Sample/ & position & density & porosity &
  thickness & scale & etching rate\\
  $I$ (mA) &$x'_n$ (cm)&  $j$ ($\text{mA}/\text{cm}^2$) & $p$
       & $d$ ($\mu\text{m}$) & $s$ & $v$ (nm/s)\\
\hline
$G_1$/ 5 &0.2 & 3.609 & 0.4943 & 0.3402 & 0.8493&  1.3608 \\
         &0.4 & 3.361 & 0.5713 & 0.3895 & 0.9789&  1.558  \\
         &0.6  & 2.884 & 0.5657 & 0.3312 & 0.9569&  1.3248 \\
         &0.8 & 2.322 & 0.5555 & 0.2732 & 0.9536&  1.0928 \\
         &1.0 & 1.799 & 0.5592 & 0.2236 & 0.9951&  0.8944 \\
         &1.2 & 1.374 & 0.5557 & 0.1886 & 0.9729&  0.7544 \\
         &1.4 & 1.056 & 0.5491 & 0.1512 & 0.9606&  0.6048 \\
         &1.6 & 0.833 & 0.5519 & 0.1238 & 0.9897&  0.4952 \\
$G_2$/10&0.2 & 7.219 & 0.5910 & 0.6347 & 0.8559&  2.5388 \\
         &0.4 & 6.723 & 0.6437 & 0.6934 & 0.9914&  2.7736 \\
         &0.6 & 5.769 & 0.6383 & 0.5907 & 0.9523&  2.3628 \\
         &0.8 & 4.645 & 0.6265 & 0.5327 & 0.9798&  2.1308 \\
         &1.0 & 3.599 & 0.5991 & 0.4587 & 0.9389&  1.8348 \\
         &1.2 & 2.749 & 0.5902 & 0.4044 & 0.9449&  1.6176 \\
         &1.4 & 2.112 & 0.5753 & 0.3378 & 0.9361&  1.3512 \\
         &1.6 & 1.666 & 0.5711 & 0.2958 & 0.9481&  1.1832 \\
$G_3$/20 &0.2 & 14.438& 0.6860 & 1.2044 & 1.1491&  4.8176 \\
          &0.4 & 13.44 & 0.7129 & 1.1931 & 1.0767&  4.7724 \\
          &0.6 &11.538 & 0.7031 & 1.0443 & 1.0588&  4.1772 \\
          &0.8 & 9.29  & 0.6258 & 0.7516 & 1.0063&  3.0064 \\
          &1.0 & 7.198 & 0.6247 & 0.5380 & 1.0104&  2.152  \\
          &1.2 & 5.498 & 0.5927 & 0.4387 & 0.9625&  1.7548 \\
          &1.4 & 4.224 & 0.5844 & 0.3633 & 0.9625&  1.4532 \\
          &1.6 & 3.332 & 0.5909 & 0.3392 & 1.0112&  1.3568 \\
\end{tabular}
\caption{\label{t:jpdv}
  Current density and fitted parameters for saveral positions on
  three samples:  porosity, thickness, scale factor and etching rate.}
\end{table}

From the data in Table \ref{t:jpdv} we can plot the fitted porosity as
a function of the calculated density current, as shown for our three
samples in Fig. \ref{fig:p}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pvsj}
  \caption{Porosity as a function of current density for three samples
    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
    thick lines. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$, joined to the other data by a thin
    line (see text). We include linear fits to the data from
    sample $G_3$ (thick straight line) and to that from all the
    samples (thin straight line). }
  \label{fig:p}
\end{figure}
Notice that for each sample the data points lie around straight lines,
except for one outlier point in each corresponding to position
$x'_1$. As discussed in Sec. \ref{sec:ps-grin-single}, those points
were very close to a wall of the electrolytic cell, so they were
affected by leakage currents towards the underside of the wall.
For this reason, we exclude those points from the following
analysis. We made a linear fit to the data from sample $G_3$ and to
the data from the three samples. A comparison shows that a fit to the
data of just one sample, $G_3$, turns out to be a reasonable predictor for the
porosity of all the samples.  From that fit we obtain that for our
preparation conditions
\begin{equation}\label{eq:p}
  p\approx 0.013\frac{\text{cm}^2}{\text{mA}} j_\perp+0.53.
\end{equation}

Similarly, we can plot the fitted etching rate as
a function of the calculated density current, as shown for our three
samples in Fig. \ref{fig:v}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{vvsj}
  \caption{Etching rate as a function of current density for three samples
    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
    thick lines. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$, joined to the other data by a thin
    line (see text). We include linear fits to the data from
    sample $G_3$ (thick straight line) and to that from all the
    samples (thin straight line). }
  \label{fig:v}
\end{figure}
As for the porosity, there are outlier points corresponding to the
immediate proximity of the wall of the cell, but the remaining points
lie on straight lines for each sample, and they
may all be approximated by a linear fit to the data of just one
sample, $G_3$, from which we get
\begin{equation}\label{eq:v}
  v\approx 0.35\frac{\text{cm}^2}{\text{mA}}
  \frac{\text{nm}}{\text{s}}j_\perp + 0.092\frac{\text{nm}}{{s}}.
\end{equation}

Using Eqs. \eqref{eq:p}, \eqref{eq:v}, \eqref{Eq:ECMR}, and
\eqref{Eq:Brugg}, we can calculate the reflectance spectra for any
desired current density $j_\perp$ and etching time. This is
illustrated in Fig. \ref{fig:Rvsjl} for the parameters that correspond
to our samples.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{jlr}
  \caption{Reflection $R$ of a PS film as a function of the current density
    current $j_\perp$ and wavelength $\lambda$ for an etching time
    $t=250\,\text{s}$. Theory (left panel) and experiment (right
    panel, see text). We indicate with the numbers 1, 2, 3 the
    data corresponding to the corresponding samples $G_1$, $G_2$ and
    $G_3$.}
  \label{fig:Rvsjl}
\end{figure}
On the right hand side of the figure we display a quilt made by
patching together the experimental reflectance data corresponding to
Figs. \ref{fig:R5}- \ref{fig:R20}, ordered according to the
corresponding current density as presented in Table
\ref{t:jpdv}. Nevertheless, for the reasons mentioned above, we
eliminated the data corresponding to position $x'_1$ on all
samples. Furthermore, as the results corresponding to sample $G_2$ in
Figs. \ref{fig:p} and  \ref{fig:v} seem shifted with respect to those
of the other samples, in order to facilitate the visualization of the
results, we artificially shifted horizontally towards the
right their contributions to Fig. \ref{fig:Rvsjl} by
$1\,\text{mA}/\text{cm}^2$. Notice that the experimental results may
be grouped along bright and dark bands and that they correspond closely to
those expected theoretically, though the experimental bands are somewhat shifted,
especially for low current densities, and the minima are not as low.

The theoretical reflectance coudl as well be calculated using
Eqs. \eqref{eq:p}, \eqref{eq:v}, \eqref{Eq:ECMR}, and
\eqref{Eq:Brugg}, for more complicated structures, in which the
current $I$ is modulated in time, allowing the design and analysis of
non-trivial multilayered GRIN PS structures.

@@
